---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# getRad

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/getRad)](https://CRAN.R-project.org/package=getRad)
[![R-CMD-check](https://github.com/enram/getRad/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/enram/getRad/actions/workflows/R-CMD-check.yaml)
[![codecov](https://codecov.io/gh/enram/getRad/branch/main/graph/badge.svg)](https://app.codecov.io/gh/enram/getRad/)
[![repo status](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
<!-- badges: end -->

The goal of `getRad` is to provide a unified interface to radar data for biological research. This is done by downloading data from repositories and loading it directly into R. Currently the functionality if focused around volume data from weather radars. However in the longer term it might also support vertical profile information, vertically integrated profile information and possibly data from other radars. 

## Installation

You can install the development version of `getRad` from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("enram/getRad")
```

For the time being the package is not yet released on CRAN.

## Usage

Here are some examples of volume data with biological information that can be downloaded.

```{r example}
library(getRad)
library(bioRad)
# Plot insect movements in Finland (Mäkinen et al. 2022)
pvol <- get_pvol("fianj", as.POSIXct("2012-5-17 14:15", tz = "UTC"))
plot(project_as_ppi(get_scan(pvol, 0), range_max = 75000))

# Spring migration in Estonia
pvol <- get_pvol("nlhrw", as.POSIXct("2023-3-19 22:15", tz = "UTC+1"))
plot(calculate_vp(pvol, h_layer = 50, n_layer = 40))
```

## Meta

- We welcome [contributions](https://enram.github.io/getRad/CONTRIBUTING.html) including bug reports.
- License: MIT
- Get [citation information](https://enram.github.io/getRad/authors.html#citation) for getRad in R doing `citation("getRad")`.
- Please note that this project is released with a [Contributor Code of Conduct](https://enram.github.io/getRad/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.
