---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# getRad

<!-- badges: start -->
[![R-CMD-check](https://github.com/enram/getRad/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/enram/getRad/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/enram/getRad/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/enram/getRad/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

The goal of getRad is to ...

## Installation

You can install the development version of getRad from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("enram/getRad")
```

## Usage

This is a basic example which shows you how to solve a common problem:

```{r example}
library(getRad)
## basic example code
```

## Meta

- We welcome [contributions](https://enram.github.io/getRad/CONTRIBUTING.html) including bug reports.
- License: MIT
- Get [citation information](https://enram.github.io/getRad/authors.html#citation) for getRad in R doing `citation("getRad")`.
- Please note that this project is released with a [Contributor Code of Conduct](https://enram.github.io/getRad/CODE_OF_CONDUCT.html). By participating in this project you agree to abide by its terms.
